Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.25in} Project Title: Development of an Intelligent Building Energy Management Platform

### 2020-11-30 proposalPres.tex
Updated proposal pres

\begin{frame}{Introduction}{}
    % Applications of Building Energy Management
    \begin{itemize}
        \item BEMS Core will interface with as many devices as it has support for 
        \begin{itemize}
            \item Wemo and Beaglebone will be fully functional by end of semester
            \item User will be able to control these devices directly from the Web Server
        \end{itemize}
        \item In the Spring, we hope to simulate a microgrid with MATLAB Simscape and an HVAC System with Simulink
        \begin{itemize}
            \item The microgrid simulation will allow us to virtually measure a power meter
            \item An HVAC System in Simulink could be controlled with a Linear Quadratic Regulator (LQR) based algorithm that can regulate the building temperature
        \end{itemize}
        \item If time allows, we will also have the BEMS Core ping a weather service for updates on severe weather as well
    \end{itemize}
\end{frame}

@@

\begin{frame}{Functional Requirements}{}
    \begin{itemize}
        \item The minimum viable product will be to connect to a Wemo Insight Smart Plug and a BeagleBone Blue
        \begin{itemize}
            \item The WeMo Plug will simply be turned on and off from the Web Server. The BEMS Core will also record its power usage
            \item The only functionality needed on the BeagleBone Blue will be PWM input to the motor drivers
        \end{itemize}
        \item A database (Apache Cassandra) will be implemented for recording power usage
    \end{itemize}
\end{frame}

@@

\begin{frame}{System Architecture - Inputs}{}
    % What are we using to build this?
    \begin{itemize}
        \item Users
            \begin{itemize}
                \item Adjust the operation of a device (turn up the temperature of an AC unit, for instance)
                \item Turn a device on or off
            \end{itemize}
        \item Smart power meters will be able to connect the platform and give real-time updates of the building's overall power usage
        \item Connected Devices
            \begin{itemize}
                \item The Wemo Switch and BeagleBone Blue will have master-slave relationship with the BEMS Core
                \item The BEMS Core will send commands through the router to download power data
            \end{itemize}
        \item The BEMS Core regularly receives weather updates from a weather service
    \end{itemize}
\end{frame}

@@

\begin{frame}{Device APIs}
    \begin{itemize}
        \item setState - Setter for Wemo Insight Switch and motor controllers on Embedded Computer
        \item getState - Returns power usage and on/off status for Wemo Insight Switch and PWM setting for Embedded Computer
        \item findDevices - Returns URL of supported devices on the network
        \item findMetadata - Returns manufacturer, name, and MAC address of supported devices
        \item For Wemo Insight Switch, IP multicasting and Universal Plug and Play are used to send messages
        \item We are using a Beaglebone Blue for an embedded computer and so far have only used IP multicasting for communication
    \end{itemize}
\end{frame}

@@

\begin{frame}{Parts List}{}
    \begin{itemize}
        \item WeMo Insight Smart Plug
        \item BeagleBone Blue
        \begin{itemize}
            \item Octavo OSD3358 Microprocessor
            \item Wifi/Bluetooth
            \item IMU/Barometer
            \item Power Regulation and state-of-charge LEDs for a 2-cell LiPo
            \item H-Bridges
            \item Connectors for 4 DC motors and 8 Servos
        \end{itemize}
        \item JST-ZH connector (for BeagleBone Blue Motor Connections)
        \item DC Motor
        \item ECE department laptop
        \item ECE department lab computers
    \end{itemize}
\end{frame}
% https://www.lucidchart.com/pages/templates/network-diagram
\begin{frame}{Timeline and Milestones}
\begin{ganttchart}[
hgrid,vgrid,x unit=.55cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{3}{16}
\gantttitle{Fall 2020}{14}\\
\gantttitle{Sep}{2}
\gantttitle{Oct}{4}
\gantttitle{Nov}{4}
\gantttitle{Dec}{4}\\
\ganttgroup[progress = 100,group progress label font = \tiny,group progress label anchor = east]{WeMo Functionality}{3}{5} \\
\ganttbar[progress = 100,bar progress label font = \tiny,bar progress label anchor = east]{Refresh Status on Web Server}{3}{5}\\
\ganttbar[progress = 100,bar progress label font = \tiny, bar progress label anchor = east]{Record Power Usage}{3}{5}\\
\ganttgroup[progress = 67,group progress label font = \tiny,group progress label anchor = east]{Data Logging Feature}{5}{10}\\
\ganttbar[progress = 80,bar progress label font = \tiny,bar progress label anchor = east]{Support for Cassandra database}{5}{9}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Matplotlib Plot in UI}{10}{10}\\
\ganttgroup[progress = 0,group progress label font = \tiny, group progress label anchor = east]{User Login}{11}{14}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Login Page}{11}{12}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Session Management}{13}{14}\\
\ganttgroup[progress = 55,group progress label font = \tiny,group progress label anchor = east]{BeagleBone Functionality}{7}{14}\\
\ganttbar[progress = 90,bar progress label font = \tiny,bar progress label anchor = east]{Communication with BEMS}{7}{11}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{PWM Motor Control}{12}{13}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Record Power Usage}{14}{14}
\end{ganttchart}
\end{frame}

\begin{frame}{Timeline and Milestones}
\begin{ganttchart}[
hgrid,vgrid,x unit=.45cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{3}{16}
\gantttitle{Spring 2021}{14}\\
\gantttitle{Jan}{2}
\gantttitle{Feb}{4}
\gantttitle{Mar}{4}
\gantttitle{Apr}{4}\\
\ganttgroup[progress = 0,group progress label font = \tiny, group progress label anchor = east]{Simscape Microgrid}{3}{8}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Setup Simscape Microgrid}{3}{5}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Get Power Meter Data}{6}{8}\\
\ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{HVAC Control}{9}{14} \\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Create HVAC system in Simscape}{9}{11} \\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Implement LQR Algorithm for HVAC Control}{12}{14} \\
\ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{Weather Service Update}{15}{16}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Receive Weather Data}{15}{15}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Display Notification}{16}{16}
\end{ganttchart}    
\end{frame}

>>>>

\begin{frame}{Introduction}{}
    % Applications of Building Energy Management
    \begin{itemize}
        \item BEMS Core will interface with as many devices as it has support for 
        \begin{itemize}
            \item Wemo and Embedded Computer will be fully functional by end of semester
            \item User will be able to control these devices directly from the Web Server
        \end{itemize}
        \item In the Spring, we hope to simulate a microgrid with MATLAB Simscape and an HVAC System with Simulink
        \begin{itemize}
            \item The microgrid simulation will allow us to virtually measure a power meter
            \item An HVAC System in Simulink could be controlled with a Linear Quadratic Regulator (LQR) based algorithm that can regulate the building temperature
        \end{itemize}
        \item If time allows, we will also have the BEMS Core ping a weather service for updates on severe weather as well
    \end{itemize}
\end{frame}

@@

\begin{frame}{Functional Requirements}{}
    \begin{itemize}
        \item The minimum viable product will be to connect to a Wemo Insight Smart Plug and a Embedded Computer (BeagleBone Blue)
        \begin{itemize}
            \item The WeMo Plug will simply be turned on and off from the Web Server. The BEMS Core will also record its power usage
            \item The only functionality needed on the BeagleBone Blue will be PWM input to the motor drivers
        \end{itemize}
        \item A database (Apache Cassandra) will be implemented for recording power usage
    \end{itemize}
\end{frame}

@@

\begin{frame}{System Architecture - Inputs}{}
    % What are we using to build this?
    \begin{itemize}
        \item Users
            \begin{itemize}
                \item Adjust the operation of a device (turn up the temperature of an AC unit, for instance)
                \item Turn a device on or off
            \end{itemize}
        \item Smart power meters will be able to connect the platform and give real-time updates of the building's overall power usage
        \item Connected Devices
            \begin{itemize}
                \item The Wemo Switch and Embedded Computer will have master-slave relationship with the BEMS Core
                \item The BEMS Core will send commands through the router to download power data
            \end{itemize}
        \item The BEMS Core regularly receives weather updates from a weather service
    \end{itemize}
\end{frame}

@@

\begin{frame}{Device APIs}
    \begin{itemize}
        \item setState - Setter for Wemo Insight Switch and motor controllers on Embedded Computer
        \item getState - Returns power usage and on/off status for Wemo Insight Switch and PWM setting for Embedded Computer
        \item findDevices - Returns IP address of supported devices on the network
        \item findMetadata - Returns manufacturer, name, and MAC address of supported devices
        \item For Wemo Insight Switch, IP multicasting and Universal Plug and Play are used to send messages
        \item We are using a Beaglebone Blue for an embedded computer and so far have only used IP multicasting for communication
    \end{itemize}
\end{frame}

@@

\begin{frame}{Parts List}{}
    \begin{itemize}
        \item WeMo Insight Smart Plug
        \item BeagleBone Blue
        \begin{itemize}
            \item Octavo OSD3358 Microprocessor
            \item Wifi/Bluetooth
            \item IMU/Barometer
            \item Power Regulation and state-of-charge LEDs for a 2-cell LiPo
            \item H-Bridges
            \item Connectors for 4 DC motors and 8 Servos
        \end{itemize}
        \item JST-ZH connector (for BeagleBone Blue Motor Connections)
        \item DC Motor
        \item ECE department laptop
        \item ECE department lab computers
    \end{itemize}
\end{frame}
% https://www.lucidchart.com/pages/templates/network-diagram
\begin{frame}{Timeline and Milestones}
\begin{ganttchart}[
hgrid,vgrid,x unit=.55cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{3}{16}
\gantttitle{Fall 2020}{14}\\
\gantttitle{Sep}{2}
\gantttitle{Oct}{4}
\gantttitle{Nov}{4}
\gantttitle{Dec}{4}\\
\ganttgroup[progress = 100,group progress label font = \tiny,group progress label anchor = east]{WeMo Functionality}{3}{5} \\
\ganttbar[progress = 100,bar progress label font = \tiny,bar progress label anchor = east]{Refresh Status on Web Server}{3}{5}\\
\ganttbar[progress = 100,bar progress label font = \tiny, bar progress label anchor = east]{Record Power Usage}{3}{5}\\
\ganttgroup[progress = 67,group progress label font = \tiny,group progress label anchor = east]{Data Logging Feature}{5}{10}\\
\ganttbar[progress = 80,bar progress label font = \tiny,bar progress label anchor = east]{Support for Cassandra database}{5}{9}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Matplotlib Plot in UI}{10}{10}\\
\ganttgroup[progress = 0,group progress label font = \tiny, group progress label anchor = east]{User Login}{11}{14}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Login Page}{11}{12}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Session Management}{13}{14}\\
\ganttgroup[progress = 55,group progress label font = \tiny,group progress label anchor = east]{Embedded Computer Functionality}{7}{14}\\
\ganttbar[progress = 90,bar progress label font = \tiny,bar progress label anchor = east]{Communication with BEMS}{7}{11}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{PWM Motor Control}{12}{13}\\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Record Power Usage}{14}{14}
\end{ganttchart}
\end{frame}

\begin{frame}{Timeline and Milestones}
\begin{ganttchart}[
hgrid,vgrid,x unit=.45cm, y unit title=.6cm,y unit chart=.4cm,milestone label font=\tiny,bar label font=\tiny, group label font=\small,bar/.append style={fill=green},bar incomplete/.append style={fill=red}]{3}{16}
\gantttitle{Spring 2021}{14}\\
\gantttitle{Jan}{2}
\gantttitle{Feb}{4}
\gantttitle{Mar}{4}
\gantttitle{Apr}{4}\\
\ganttgroup[progress = 0,group progress label font = \tiny, group progress label anchor = east]{Simscape Microgrid}{3}{8}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Setup Simscape Microgrid}{3}{5}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Get Power Meter Data}{6}{8}\\
\ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{HVAC Control}{9}{14} \\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Create HVAC system in Simscape}{9}{11} \\
\ganttbar[progress = 0,bar progress label font = \tiny,bar progress label anchor = east]{Implement LQR Algorithm for HVAC Control}{12}{14} \\
\ganttgroup[progress=0,group progress label font=\tiny,group progress label anchor = east]{Auto Discovery}{15}{16}\\
\ganttgroup[progress = 0,group progress label font = \tiny,group progress label anchor = east]{Weather Service Update}{15}{16}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Receive Weather Data}{15}{15}\\
\ganttbar[progress = 0,bar progress label font = \tiny,group progress label anchor = east]{Display Notification}{16}{16}
\end{ganttchart}    
\end{frame}
